Figures

### 2019-05-17 figures/10_nitrogen_deposition.Rmd
move ndep analysis to seprate file

dt_tp <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  arrange(desc(abs(tp))) %>%
  data.frame() %>%
  dplyr::select(rowname, tp, tn)

dt_tn <- dt_tp %>% 
  arrange(desc(abs(tn))) %>% 
  data.frame()

dt_tp_rows <- dt_tp$rowname
dt_tp <- dt_tp %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tp) <- dt_tp_rows

dt_tn_rows <- dt_tn$rowname
dt_tn <- dt_tn %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tn) <- dt_tn_rows

# ---- heatmap ----
dt_tp_hmap <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  # janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  data.frame()

dt_tp_rows       <- dt_tp_hmap$rowname
dt_tp_hmap            <- dt_tp_hmap %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tp_hmap) <- dt_tp_rows

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)

# ---- dotplot ----

@@

plot_opts <- theme(axis.title.y = element_blank(), 
                   axis.text = element_text(size = 8))
plot_grid(
  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = var)) + 
    plot_opts, 
  ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = var)) +
    plot_opts
)

# ---- densityplots ----
library(ggforce)

ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
ggplot(data = tidyr::gather(dt_sub)) + 
  geom_density(aes(value)) +
  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)

>>>>

plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
     lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)

ggplot(data = dt_sub) + 
  geom_point(aes(x = ))

slice_cormat <- function(var_name, dt_sub){
  # var_name <- "nitrogen_atmospheric_deposition"

  dt_corr <- dt_sub %>%
    corrr::correlate() %>%
    # corrr::shave() %>%
    janitor::remove_empty(c("rows", "cols")) %>%
    mutate_if(is.numeric, round, 2) %>%
    arrange(desc(abs(!!rlang::sym(var_name)))) %>%
    data.frame() %>%
    dplyr::select(rowname, var_name)

  dt_corr_rows <- dt_corr$rowname
  dt_corr <- dt_corr %>%
    dplyr::select(-rowname) %>%
    mutate_all(abs)
  row.names(dt_corr) <- dt_corr_rows

  dt_corr
}

@@

dt_ndep <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)

ggplot(data = prep_dotplot(dt_ndep, "nitrogen_atmospheric_deposition")) +
    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
    plot_opts
